A Kleisli-like construction for Parametric Monads, with Examples

### 2018-11-09 effects/effects.tex
Modified abstract.

\begin{abstract}
\keywords{denotational semantics, category theory, game semantics}
\end{abstract}

>>>>

\begin{abstract}
  A well-known principle in denotational semantics is that adding an effect to a categorical model should correspond to the Kleisli category construction for some suitable monad.  
  Our point of departure is the observation that much recent work in semantics, particularly in game semantics, has broken away from this principle by modelling effects using categories that are not Kleisli categories.  
  Our aim is to extend the theory of monadic effects to these models in a systematic way.

  An important part of our approach will be to study parametric monads, otherwise known as lax actions of monoidal categories.
  These generalize monads: a monad is precisely an action of the trivial category.
  We introduce a construction on parametric monads which takes a parametric monad on a category and gives us back a new category.  
  As with the Kleisli category, the objects of this category will be the objects of the original category, while the morphisms are obtained from morphisms in the original category in a formal manner brought about by the action.  
  We show that this new construction is closely related to existing models of effects in game semantics, allowing us to reason systematically about adequacy and full abstraction proofs.

  We illustrate the relevance of this construction by showing that a special case gives us a fully abstract game semantics for Probabilistic Algol, which can be related to the existing model given by Danos and Harmer.
\keywords{denotational semantics, category theory, game semantics}
\end{abstract}
